D3692R1: How to Avoid OOTA Without Really Trying

### 2025-06-14 paper/ootavacuous.tex
ootavacuous: Clarify non-semantic dependency in Section 2.2.2
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Cite P3064R2 Appendix B for gcc command line
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Suppose that in some execution of the previous example,
both \co{x} and \co{y} are zero.
Then changes to either \co{x} or \co{y}
will not cause a change in the value stored to \co{z}.
In other words, in this execution there is no semantic dependency
from either \co{x} or \co{y} to \co{z}.
But there \emph{is} a semantic dependency from the \emph{pair}
\{\co{x},~\co{y}\} to \co{z},
because changes to both \co{x} and \co{y}
can cause the value stored in \co{z} to change.
This means that, prior work~\cite{PaulEMcKenney2016OOTA}
notwithstanding, accurate definitions of sdep cannot always rely on
single-variable perturbations;
they must at times consider changes to multiple variables.
% @@@  Pull anything in?  Doesn't seem necessary.
% See Appendix~\ref{app:Non-Trivial Semantic Dependencies}
% for examples and additional discussion.

@@

The exact definition of a computer language is a subject of some debate,
with standards, implementations, and users all having their own
influence~\cite{KayvanMemarian2016DepthOfC-1,KayvanMemarian2016DepthOfC-2},
and each being prone to change over time.
In areas that are not well settled or where users might reasonably
want to resist the dictates of the standard,
compilers often provide switches to override their default behaviors.
An example is GCC's \co{-funsigned-char} command-line argument,
which causes it to treat variables of type \co{char} as unsigned
(see Section~\ref{sec:Semantic Dependencies and Architectural Variations}).
Many more examples of user control over language semantics
may be found through use of the command \co{make V=1}
in a Linux-kernel source tree and by the discussion
in~\cite{KayvanMemarian2016DepthOfC-1,KayvanMemarian2016DepthOfC-2}.

>>>>

Suppose that in some execution of the previous example,
both \co{x} and \co{y} are zero.
Then a change to exactly one of \co{x} or \co{y}
will not cause a change in the value stored to \co{z}.
In other words, in this execution there is no semantic dependency
from either \co{x} or \co{y} to \co{z}.
But there \emph{is} a semantic dependency from the \emph{pair}
\{\co{x},~\co{y}\} to \co{z},
because changes to both \co{x} and \co{y}
can cause the value stored in \co{z} to change.
This means that, prior work~\cite{PaulEMcKenney2016OOTA}
notwithstanding, accurate definitions of sdep cannot always rely on
single-variable perturbations;
they must at times consider changes to multiple variables.
% @@@  Pull anything in?  Doesn't seem necessary.
% See Appendix~\ref{app:Non-Trivial Semantic Dependencies}
% for examples and additional discussion.

@@

The exact definition of a computer language is a subject of some debate,
with standards, implementations, and users all having their own
influence~\cite{KayvanMemarian2016DepthOfC-1,KayvanMemarian2016DepthOfC-2},
and each being prone to change over time.
In areas that are not well settled or where users might reasonably
want to resist the dictates of the standard,
compilers often provide switches to override their default behaviors.
An example is GCC's \co{-funsigned-char} command-line argument,
which causes it to treat variables of type \co{char} as unsigned
(see Section~\ref{sec:Semantic Dependencies and Architectural Variations}).
Many more examples of user control over language semantics
may be found through use of the command \co{make V=1}
in a Linux-kernel source
tree~\cite[Appendix B]{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
and by the discussion
in~\cite{KayvanMemarian2016DepthOfC-1,KayvanMemarian2016DepthOfC-2}.
